---
title: "**FINAL REPORT**"
subtitle: "RMED901"
author: "MEMBERS OF GROUP 3"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
---

<style type="text/css">

body, td {
   font-size: 18px;
}
code.r{
  font-size: 12px;
}
pre {
  font-size: 12px
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>
<br>

## **Introduction**

The main objective of this group project was to put knowledge from the course (RMED901) into practice. The group was given a set of different tasks to be solved individually or in collaboration. The tasks included coding by using RStudio, tidying and wrangling data, creating plots and finally analyze the results. A repository created on GitHub was used for collaboration and version control.<br>
<br>
<br>

## **GitHub Repository**

First we created a Rprojects in RStudio, and then a GitHub Repository. The latter made it possible to store and share script/files, and also track revision history:<br>
https://github.com/MarianneHannisdal/GROUP3 <br>
<br>
The repository contains the following main folders:<br>
<br>

- DATA (original and tidied dataset/original and updated codebook)<br>
- SCRIPTS (code used for tidying, creating plots and analyzing the data)<br>
- RESULTS (final report)<br>
<br>
<br>

## **Datasource**




<br>
<br>

## **Tidy, adjust and explore**

To tidy the dataset, we had to:

- remove duplicated rows
- rename columns that contain spaces, punctuation signs or start with numbers (e.g.'X1_Age' to 'Age') 
- rename columns to more intuitive names (e.g. 'Units' to 'Allogeneic.units')
- separate columns (e.g. 'subject' to 'subject' + 'Hospital')
- reshape values in columns including various measurements (e.g. 'TimeToRecurrence-unit' into days)<br>
<br>

To manipulate/wrangle the data, we had to:

- remove unnecessary columns from the dataframe ('AA', 'bGS' 'BNplus' and 'OrganConfined)
- change variable types ('subject' from character to numeric)
- create a set of new columns (e.g. 'recurrence' to return the values Yes or No) 
- change and arrange the order of some columns 
- organize the R code in a pipe
- join an additional dataset to the tidied dataset<br>
<br>

The tidied and manipulated dataset was saved in a new file and the codebook was updated.<br>
Now, the new file contains 316 number of observations and 21 number of variables.<br>
<br>
To explore the data, we had to:<br>


- count columns with missing variables (number of columns containing NA = 7)
- stratify the data by a categorical column ('TimeToRecurrence_days' grouped by 'T.stage') 
- calculate minimum and maximum levels, mean and sd for several conditions and create a table<br>
<br>

All the scripts were eventually styled by using [{styler}](https://styler.r-lib.org/).<br>
A README file was written to document the contents and structure of the repository on GitHub.<br>
<br>
<br>




## **Create plots**
In this chapter we would like to present some of the plots we created to answer questions given in the exam description. 



```{r cars}
summary(cars)
```




```{r}

```



## **Analysing the data**




```{r pressure, echo=FALSE}
plot(pressure)
```

## **Conclusion**

<br>
<br>

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
